25 years of Social Work Research

### 2015-02-25 Analysis.Rmd
Fixed analysis.

---
title: 'The History of Social Work Research: A Data Science Perspective'
output: pdf_document
---

# Data harvesting

Data collection for this study was separated into three phases.

## Search Query

The first phases involved querying three different databases serviced by the EbscoHost web platform: psycInfo, Social Science Abstract, and Social Work Abstracts.  These databases were selected because they provide the indexing services for the majority of social work journals.  Additionally, search queries from these databases, served by EbscoHost, allowed search results to be exported raw text (*.txt) documents, referred to as a _generic bibliographic format_.  Other databases and search engines (e.g., Google Scholar) were not queried because the results could not be saved in a common format.  This is a limitation of the study that is covered in the discussion section.

The search began by querying each database for every _journal article_ from every journal that was included in the list by Hodge and ... [Describe this list] ... Each query was performed independently on each database,

We had a three-level search process designed to be as comprehensive as possible.  First, we began by running a separate search query on each database for every journal contained in the list by Hodge.  We then conducted a subsequent search of all journal titles based on the following key words:

+ social work
+ social welfare
+ social casework 
+ social case work
+ social service
+ human service
+ social development 
+ social environment

In each query, results were limited to only journal articles, which excluded other document types including (but not limited to) editorials, book reviews, software reviews, and obituaries.  All searches were conducted between January 24, 2015 and January 30, 2015. Results were subsequently filtered to exlclude years 2014 and 2015 due to delays in indexing.  Search results were exported from EbscoHost platfrom into a _generic bibliographic format_.  This is an unstructured text file (*.txt) that was processed using in R.  The multiple searches were then transformed into an analyzable database using a customized script developed by the first two authors of the study (BEP and BGV).

Study authors reviewed all journal titles and

# Data Pre-Processing

# NOTE: CONFIRM THAT SOCIAL CASEWORK IS SAME AS FAMILIES IN SOCIETY.  ENSURE WE 
# HAVE THE ARTICLES FOR WHEN THE JOURNAL WAS ALSO CALLED THE FAMILY

```{r initialization_dataprocessing, warning=FALSE, message=FALSE, eval=FALSE}
# Clear workspace
rm(list=ls())

@@

# Set the working directory to store files created by BWR functions
path <- "/Users/beperron/Git/SocialWorkResearch/Data"

# Wrangle the data with the BWR function suite
ebscoBWR.f(csv=FALSE, path=path, psycInfoOnly = FALSE)
save(bwr.df, file = "fullDF.R")
```

#add no authorship indicated
#Anonymous
x.temp <- filter(bwr.df, attributes == "article")
x.temp2 <- filter(bwr.df, attributes == "journal")

x.temp3 <- filter(bwr.df, attributes == "author")
b <- grepl("@", x.temp3$record)

test.case <- filter(bwr.df, attributes == "AU")
auth.name <- filter(test.case, grepl("(Perron,\\sB)", record))

x.temp <- filter(bwr.df, attributes == "KW" | attributes == "KP")

```{r initialization_analysis, message=FALSE, warning=FALSE, comment=NA}
rm(list=ls())
setwd("/Users/beperron/Git/SocialWorkResearch/Data")
source("/Users/beperron/Git/BibWrangleR/functions/ggsurv.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/HistoricalArticles.R")

library(dplyr)
library(ggplot2)
library(gridExtra)
library(survival)
library(grid)
library(png)
library(reshape2)

# Inspect dimensions of the data file (Rows X Columns)
dim(bwr.df)

# Inspect variable names of the data file
names(bwr.df)

# How many unique article titles?  Ebsco Results of most current search is $n=XXXX$. Do not proceed with analysis if the output does not match this result.  
length(which(bwr.df$attributes == "TI"))
```

# Exclude years 2014 and 2015

```{r}
years <- c("2014", "2015")
ebsco.remove <- bwr.df[bwr.df$record %in% years, ]
ebsco.remove <- ebsco.remove[, "articleID"]
bwr.df <- bwr.df[!(bwr.df$articleID %in% ebsco.remove),]
```

# Merge journal titles

```{r}
bwr.df$record <- ifelse(bwr.df$record == "Eugenics and Social Welfare Bulletin", 
                       "Eugenics & Social Welfare Bull.", 
                        bwr.df$record)

bwr.df$record <- ifelse(bwr.df$record == "The British Journal of Social Work", 
                       "British Journal of Social Work", 
                        bwr.df$record)

bwr.df$record <- ifelse(bwr.df$record == "Social Work & Social Sciences Review", 
                       "Social Work and Social Sciences Review", 
                        bwr.df$record)

bwr.df$record <- ifelse(bwr.df$record == "Social Work with Groups", 
                       "Social Work With Groups", 
                        bwr.df$record)

bwr.df$record <- ifelse(bwr.df$record == "Computers in Human Services", 
                       "Journal of Technology in Human Services", 
                        bwr.df$record)

bwr.df$record <- ifelse(bwr.df$record == "Journal of Sociology & Social Welfare", 
                       "Journal of Sociology and Social Welfare", 
                        bwr.df$record)

#Note leave space after the (Electronic only)
bwr.df$record <- ifelse(bwr.df$record == "Contemporary Rural Social Work (Electronic only) ", 
                        "Contemporary Rural Social Work (Electronic only) ", bwr.df$record)

```

# Journals excluded from search results.

```{r}
exclusions <- c(
    "American Journal of Preventive Medicine", 
    "Behavior Modification", 
    "Brain and Cognition",
    "Canadian Journal of Community Mental Health",
    "Canadian Journal on Aging",
    "Early Child Development and Care",
    "Early Education and Development",
    "Employee Assistance Quarterly",
    "Evaluation and Program Planning",
    "General Hospital Psychiatry",
    "Hospital Social Service",
    "International Review of Social Research",
    "Journal of Applied Behavioral Science",
    "Journal of Applied Rehabilitation Counseling",
    "Journal of Community & Applied Social Psychology",
    "Journal of Health & Human Services Administration",
    "Journal of Nonverbal Behavior",
    "Learning Disabilities Research & Practice",
    "New York State Department of Social Welfare, Division Publication",
    "Pennsylvania Social Work",
    "Proceedings of the National Converence of Social Work",
    "PROFILE Issues in Teachers' Professional Development",
    "Psychotherapy",
    "Social Service Department, Presbyterian Hospital, New York",
    "Social Work Technique",
    "Social Work Today", # Magazine
    "Social Work Yearbook",
    "The New Social Worker",
    "Systems Research and Behavioral Science",
    "Teaching and Teacher Education",
    "University of Chicago Social Service Monograph",
    "The Scientific Review of Mental Health Practice",
    "The Clinical Supervisor",
    "University of Chicago Social Service Monograph")
ebsco.remove <- bwr.df[bwr.df$record %in% exclusions, ]
ebsco.remove <- ebsco.remove[, "articleID"]
bwr.df <- bwr.df[!(bwr.df$articleID %in% ebsco.remove),]
```

```{r unique_titles, echo=FALSE}
unique.titles <- filter(bwr.df, attributes == "SO") %>%
    group_by(record) %>%
    summarise(
        N = n())
```

# Preliminary Analyses

## Summary of all journal titles included in the analysis

To do:

+ In the table, include the first and last years of indexing, and the numbers of articles.  
+ Write the script to output a *.csv file so that it can be included as an Appendix without any formatting.

```{r unique_titles, echo=FALSE}
unique.titles <- filter(bwr.df, attributes == "SO") %>%
    group_by(record) %>%
    summarise(
        N = n())

title <- bwr.df %>%
        filter(attributes == "SO") %>%
        select(id = articleID, SO = record)

article <- bwr.df %>%
        filter(attributes == "TI") %>%
        select(id = articleID, journal.title = record)

title.articles <- title %>% 
        left_join(article) %>%
        group_by(title)

# Number of unique titles
number.journals <- length(unique(unique.titles$record))

# Unique titles
journals.unique <- unique(unique.titles$record)
#write.csv(journals.unique, "journals.csv")

number.journals
sort(journals.unique)
socialWorkJournals <- journals.unique
#save(journals.unique, file="socialWorkJournals.R")
```

## Count of unique journal titles over time

To do:
+ Integrate the full journal listing of EbscoHost 
+ Plot overall number of journals over time 
+ Plot overall number of journals by major discipline category as defined by EbscoHost classification -- use sociology, anthropology, economics, psychology, and political science
+ The following "overall growth" plot excludes social work journals in this study.  There were a small number of overlap journals between social science and social work journals (N = 4 -- double check for final analysis.  The journals that overlapped were included in the social work group.

```{r unique_titles_year, message=FALSE, comment=NA, warning=FALSE, echo=FALSE}
journals.year <- tbl_df(bwr.df)

year <- journals.year %>%
        filter(attributes == "YR") %>%
        select(id = articleID, year = record)

journals <- journals.year %>%
        filter(attributes == "SO") %>%
        select(id = articleID, journal.title = record)

n.journals.year <- journals %>% 
        left_join(year) %>%
        group_by(year) %>%
        distinct(journal.title) %>%
        summarise(n = n())

journal.count <- ggplot(n.journals.year, aes(as.numeric(year), y=n, group=1)) + 
    geom_line(colour="darkblue") +
    #geom_point(colour="red") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
    xlab("Publication year") + 
    ylab("Number") + 
    ggtitle("Number of Journals Over Time") + 
    scale_x_continuous(breaks=seq(1914, 2014, 5))

journal.count
```

## Growth of Social Work compared to growth of the social sciences

This section shows the overall growth of the social sciences.  This includes all _academic journals_ (excluding magazines and trade publications) that have the following discipline tag:

+ Sociology
+ Psychology
+ Economics
+ Political Science & Studies
+ Economics
+ Anthropology

```{r echo=FALSE}
ebscoFullListing.df <- ebscoFullListing.df[ebscoFullListing.df$SourceType == "Academic Journal",]
ebscoFullListing.df$IndexingStart <- format(as.Date(ebscoFullListing.df$IndexingStart, "%m/%d/%Y"), "%Y")
ebscoFullListing.df$IndexingStop <- format(as.Date(ebscoFullListing.df$IndexingStop, "%m/%d/%Y"), "%Y")
ebJournals.df <- ebscoFullListing.df %>% filter(SourceType == "Academic Journal") %>%
    select(Discipline, IndexingStart, IndexingStop, PublicationName, ISSN) %>%
    mutate(IndexingStart = as.numeric(IndexingStart), IndexingStop = as.numeric(IndexingStop)) %>%
    filter(Discipline == "Sociology" | Discipline == "Political Science & Studies"| 
           Discipline == "Psychology"| Discipline == "Economics" | Discipline == "Anthropology") 
```

Some of the journals have duplicate entries in the database because they are cross-classified in multiple social science disciplines.  The following code is used to create a data set that excludes duplicate entries in the database and ensures no overlap between the social science list and the social work list of journals. Duplicates are identified based on ISSN, not journal title.  This will ensure all duplicates are identified.

```{r}
ebJournals.df.issn <- ebJournals.df %>% select(ISSN)
ebJournals.df.unique <- !duplicated(ebJournals.df.issn)

#This function here tests whether the duplication identifier correctly gets the first unique record (by assigning TRUE) and then excluding subsequent records (by assigning FALSE) 
#cbind(ebJournals.df.unique, ebJournals.df.issn$ISSN)

#This subsets out the duplicates
ebJournals.df.no.duplicates <- ebJournals.df[ebJournals.df.unique, ]

#This function does a logical comparison of the social science journals and the social work journals to determine potential overlap.  
overlap <- ebJournals.df.no.duplicates[(ebJournals.df.no.duplicates$PublicationName %in% journals.unique),]  
print(overlap)

#This reduces the overlap from the social science journal lists, retaining the overlap in the social work journals
ebJournals.df.no.overlap <- ebJournals.df.no.duplicates[!(ebJournals.df.no.duplicates$PublicationName %in% journals.unique),]   
```

This section uses the `melt` function to transform the social science data file into a format that can be plotted using ``ggplot2`.  
```{r echo=FALSE}

#Remove variables that will interfere with melting procedure
socialScienceJournals.df <- ebJournals.df.no.overlap %>% 
    select(-PublicationName, -ISSN) %>%
    mutate(journalID = c(1:nrow(ebJournals.df.no.overlap))) %>%
    mutate(journalID = as.factor(journalID)) %>% 
    select(-Discipline)

socialScienceJournals.melted <- melt(socialScienceJournals.df)

ebJournals.overtime.start.d <- socialScienceJournals.melted %>% 
    filter(value = !is.na(value)) %>%
    group_by(value) %>%
    summarise(N.start = n())

ebJournals.overtime.end.d <- socialScienceJournals.melted %>%
    filter(variable == "IndexingStop"  & !is.na(value)) %>%
    group_by(value) %>%
    summarise(N.end = n())

ebjournals.joined.d <- left_join(ebJournals.overtime.start.d, ebJournals.overtime.end.d) %>%
    mutate(N.end = ifelse(is.na(N.end), 0, N.end), Cumulative = cumsum(N.start)) %>%
    mutate(N.adjusted = Cumulative - N.end)

journal.time.reduced <- n.journals.year %>% filter(year >= 1950)
ggplot() + 
    geom_line(data = ebjournals.joined.d, aes(x=value, y=N.adjusted), group=1, colour="purple") + 
    geom_line(data = journal.time.reduced, aes(as.numeric(year), y=n), group=1, colour="darkblue")
```

## What journals published the most number of articles

```{r journal_output, echo=FALSE}

n.so.yr <- filter(bwr.df, attributes == "SO" | attributes == "YR")

n.so <- filter(bwr.df, attributes == "SO") %>% mutate(title = record) %>% 
        select(-attributes, -record)

n.yr <- filter(bwr.df, attributes == "YR") %>% mutate(year = record ) %>% 
        select(-attributes, -record)

n.so.yr <- left_join(n.so, n.yr) %>%
    group_by(title) %>%
    summarise(first = min(year), last = max(year), n.to.date = n()) %>%
    arrange(desc(n.to.date))

# 10 highest number of publications
head(n.so.yr, 20)
```

## What is the lifespan of journals?

To do:
+ Incorporate all EbscoHost journals and the separate disciplinary journals

```{r journal_lifespan, echo=FALSE}
#10 longest running journals 
longest.running <- n.so.yr %>%
       mutate(last = as.numeric(last), first = as.numeric(first), 
              year.diff = last - first) %>%
       arrange(desc(year.diff)) %>%
       select(title, first, last, year.diff) %>%
       mutate(stop = year.diff, event = ifelse(as.numeric(last) != 2013, 1, 0)) %>%
       select(title, stop, event, as.numeric(first))

survival.journals <- survfit(Surv(longest.running$stop+1, longest.running$event) ~ 1)
median.survival <- data.frame(time = c(24,24), quant = c(.5,0))

head(longest.running)

ggsurv(survival.journals) + 
    #geom_line(data = median.survival, aes(time, quant), linetype="longdash") +
    #annotate("segment", x = 32, xend = 27, y = .12, yend = .12, size = .25, arrow =arrow()) +
    #geom_text(x = 45, y =.12, label = "median survival", size = 4) + 
    geom_text(x = 75, y =.75, label = "+ = Last year of indexing", size = 4) +
    ylim(0,1) +
    xlim(0,50) + 
    xlab("Survival Time (in years)") +
    ylab("Survival Probability") +
    ggtitle("Survival Probability of Social Work Journals")

```

## What is the number of articles published per year

To do:
+ Plot against major disciplinary categories

```{r articles_per_year, echo=FALSE}
n.articles.year <- filter(bwr.df, attributes == "YR") 
year.split <- split(n.articles.year, n.articles.year$record)
year.count <- unlist(lapply(year.split, nrow))
year.count <- year.count[order(names(year.count))]
years <- names(year.count)

df <- data.frame(years, year.count)
rownames(df) <- NULL

plot.article.count <- ggplot(df, aes(as.factor(years), 
                    y = year.count, group=1)) + 
    geom_line(colour="black") +
    #geom_point(colour="red") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
    xlab("year") + 
    ylab("count") + 
    ggtitle("Number of Studies by Year") +
    scale_x_discrete(breaks=c(seq(1914, 2015, 10))) +
    scale_y_continuous(breaks = c(seq(0, 2000, 250)))

df$years <- as.numeric(as.character(df$years))

plot.article.cumulative <- ggplot(df, aes(x = years, y = cumsum(year.count))) + 
    geom_line() + 
    theme(axis.text.x = element_text(angle=45, hjust=1)) +
    scale_x_continuous(breaks=pretty(df$years)) +
    xlab("year") +  
    ylab("count") +
    scale_x_continuous(breaks = c(seq(1914,2014,10))) +
    scale_y_continuous(breaks = c(seq(0, 25000, 2500))) + 
    ggtitle("Cumulative Frequency")

grid.arrange(plot.article.count, plot.article.cumulative, ncol=2)

# Print most recent ten years
tail(df, 10)
```

# What are the most frequent topic areas (by author specified keywords)?

To do:  
+ Fix script that performs matching -- convert all keywords to lower before matching

```{r keywords_overall, comment=NA, warning=FALSE, message=FALSE, echo=FALSE}
kp.df <- filter(bwr.df, attributes == "KP")

subject.terms <- stringr::str_split(kp.df$record, pattern = ";")
subject.terms <- tolower(subject.terms)
subject.terms <- unlist(lapply(subject.terms, function(x) gsub(" ", "", x)))
subject.terms.total <- length(unlist(lapply(subject.terms, 
                        function(x) gsub(" ", "", x))))

subject.terms.unique <- length(unique(subject.terms))

subject.terms.l <- list(subject.terms.total = subject.terms.total,
                      subject.terms.unique = subject.terms.unique)

most.frequent <- as.data.frame(table(subject.terms))

most.frequent <- arrange(most.frequent, desc(Freq))

# Print summary statistics
print(subject.terms.l)

# Print 25 most frequent
head(most.frequent, 25)
```

## Most Frequent Author Keywords

_DO NOT INTERPRET RESULTS HERE THIS SECTION IS NOT WORKING PROPERLY_

For this analysis (to-do), select a few keywords that may tell an interesting story of how they change over time -- something that might be revealing of 'trends.'

```{r keywords_over_time, warning=FALSE, message=FALSE, echo=FALSE}
kp.yr <- filter(bwr.df, attributes == "YR") %>%
    mutate(year = as.numeric(record)) %>% select(-record, -attributes)

kp <- bwr.df %>%
        filter(attributes == "KP") %>%
        select(articleID = articleID, keyword = record) %>%
        mutate(keyword = gsub(" ", "", keyword))

kp.year <- kp %>% 
         left_join(kp.yr) %>%
         group_by(keyword, year) %>%
         summarise(n = n()) %>%
         arrange(keyword, year, n)

select.keywords <- c("women", "leadership")
select.keywords.df <- kp.year %>% filter(tolower(keyword) %in% select.keywords)

library(plyr) # Fix code so ply loads before dplyr
key.plot.df <- ddply(select.keywords.df, .(keyword), transform, cumulative = cumsum(n))
detach(package:plyr)

#Fix graph to sort the keywords / colour
ggplot(key.plot.df, aes(x = year, y = cumulative, colour = keyword, group = keyword)) + 
    geom_line() +
    ggtitle("Cumulative Sum of Articles by Keywords") +
    ylab("Cumulative Sum") + 
    xlab("Year") + 
    theme(legend.title=element_blank())

```

## Location of Studies

To do:
+ Determine best format / presentation of map

```{r location, comment=NA, warning=FALSE, message=FALSE, echo=FALSE}
LO.df <- filter(bwr.df, attributes == "LO") %>%
         group_by(record) %>%
         summarise(Country = unique(record),
                   N = n()) %>%
        arrange(desc(N)) %>% 
        select(-record)

locations <- as.data.frame(table(LO.df))
locations <- arrange(locations, desc(Freq))
locations.unique <- length(unique(locations))

#write.csv(locations, "location.csv")

```

## Location of studies over time

To do:
+ Determine best format / presentation of map

```{r location_over_time, warning=FALSE, message=FALSE, echo=FALSE}
library(RColorBrewer)
year <- filter(bwr.df, attributes == "YR") %>%
    mutate(year = as.numeric(record)) %>% select(-record, -attributes)

location.temp <- bwr.df %>%
        filter(attributes == "LO") %>%
        select(articleID = articleID, country = record) %>%
        mutate(country = gsub(" ", "", country))

location.year <- location.temp %>% 
         left_join(year) %>%
         group_by(country, year) %>%
         summarise(n = n()) %>%
         arrange(country, year, n) %>%
         mutate(cumsum_n = cumsum(n), log_n = log(n+1))

top.locations <- LO.df %>% 
                 select(Country) %>%
                 slice(1:5)

top.locations$Country <- gsub(" ", "", top.locations$Country)

location.year.top <- location.year %>% filter(country %in% top.locations$Country)

ggplot(location.year.top, aes(x = year, y = log_n, colour = country )) + 
    geom_line() +
    ggtitle("Log Number of Articles by Countries With Highest Scholarly Ouput") +
    xlab("Publication Year") + 
    ylab("log N+1") +
    theme(legend.position=c(.210, .7))

top.locations.no.us <- LO.df %>% 
                select(Country) %>%
                slice(2:10)

top.locations.no.us$Country <- gsub(" ", "", top.locations.no.us$Country)

location.year.top.no.us <- location.year %>% filter(country %in% top.locations.no.us$Country)

ggplot(location.year.top.no.us, aes(x = year, y = cumsum_n, colour = country )) + geom_line() +
    ggtitle("Cumulative Number of Article by Countries with Highest Scholarly Output \n(Excluding the United States)") +
    theme(legend.position=c(.210, .6))
```
## Countries represents in the social work research

To do:
+ Obtain definition of `LO` tag.  
+ Determine how many articles had LO tag (note the issue if not included from Social Science Index)

```{r fig.width=8, echo=FALSE}
Map100YearWithUS <- readPNG("/Users/beperron/Git/SocialWorkResearch/images/Map100Years.png")
grid.raster(Map100YearWithUS)

Map100YearWithoutUS <- readPNG("/Users/beperron/Git/SocialWorkResearch/images/Map100YearsWithoutUS.png")
grid.raster(Map100YearWithUS)
```

## Countries not represented in social work research

```{r fig.width=8, echo=FALSE}
library(png)
library(grid)
img <- readPNG("/Users/beperron/Git/SocialWorkResearch/images/NotRepresented100Years.png")
grid.raster(img)

```

## Number of authors
```{r comment=NA, message=FALSE, warning=FALSE, echo=FALSE}
n.authors.article <- bwr.df %>% 
    filter(attributes == "AU") %>%
    select(id = articleID, author= record) %>%
    mutate(id = as.numeric(id))

n_authors.1 <- n.authors.article %>% 
        group_by(id) %>%
        summarise(n = n())

n_authors.1t <- n_authors.1 %>% mutate(n = ifelse(n >=6, 6, n)) %>% 
    group_by(n) %>%
    summarise(Articles = n())

ggplot(n_authors.1t, aes(x = n, y = Articles)) +
    geom_bar(stat="identity", colour="black", fill = "white") +
    geom_text(aes(label = Articles), vjust=-.3, size = 4) +
    scale_x_discrete(limits = c(as.character(1:5), "6+")) + 
    ggtitle("Number of Articles by Author Count") + 
    xlab("Author Count") + 
    ylab("Articles")
```

## Number of authors over time

This figure shows the average number of authors, along with the standard deviation as the ribbon around the average.  Note that there is a possible problem in these data, with a single article listing a huge number.  That can be corrected at a later time.

```{r message=FALSE, comment=NA, warning=FALSE, fig.height=2, fig.height=4, echo=FALSE}
df.2 <- tbl_df(bwr.df)
year <- df.2 %>%
        filter(attributes == "YR") %>%
        select(id = articleID, year = record)

authors <- df.2 %>%
        filter(attributes == "AU") %>%
        select(id = articleID, author = record)

n_authors <- authors %>%
        group_by(id) %>%
        summarise(n=n())

n_authors <- n_authors %>% 
        left_join(year) %>%
        group_by(year) %>%
        summarise(median.n = median(n),
                  average.n = mean(n),
                  min.n = min(n),
                  max.n = max(n),
                  std.dev  = sd(n) )

plot.author.count2 <- ggplot(n_authors, aes(as.numeric(year), y=average.n, group=1)) +  
    geom_ribbon(aes(ymin = average.n-std.dev, ymax=average.n+std.dev), colour="lightblue", fill="lightblue", alpha=.40) +
    geom_line(colour="black") + 
    geom_segment(aes(x= 1940, y = 5.5, xend = 1935, yend = 5.5), 
                 arrow=arrow(length=unit(0.25, "cm"))) +
    annotate("text", x = 1951, y = 5.5, label = "1 outlier case of \n24 listed authors", size=3.5) +
    ylab("Average number of authors (black) \nStandard deviation (light blue)") +
    xlab("Publication year") +
    ggtitle("Average Number of Authors per Article Over Time")

plot.author.count2

```

```

>>>>

---
title: "Object Maker"
output: pdf_document
---

# Ebsco Full

```{r warning=FALSE, message=FALSE, eval=TRUE}
# Clear workspace
rm(list=ls())

@@

# Set the working directory to store files created by BWR functions
path <- "/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL"

# Wrangle the data with the BWR function suite

ebscoBWR.f(csv=FALSE, path=path, psycInfoOnly=FALSE)
save(ebscoBWR.df, file = "ebscoFULL.R")
```

# PsychInfo Only

```{r warning=FALSE, message=FALSE, eval=TRUE}
# Clear workspace
rm(list=ls())

# Set the working directory to store files created by BWR functions
path <- "/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo"

# Wrangle the data with the BWR function suite

ebscoBWR.f(csv=FALSE, path=path, psycInfoOnly=TRUE)
save(ebscoBWR.df, file = "PsychInfo.R")
```

# ProQuest

```{r warning=FALSE, message=FALSE, eval=TRUE}
# Clear workspace
rm(list=ls())

# Read BWR functions for Mac OS
source("/Users/beperron/Git/BibWrangleR/functions/proquestBWR.R")

# Set the working directory to store files created by BWR functions
path <- "/Users/beperron/Git/SocialWorkResearch/Data/ProQuest"

# Wrangle the data with the BWR function suite

proQuestBWR.f(csv=FALSE, path=path)
save(proQuestBWR.df, file = "ProQuest.R")
```

### 2015-02-25 dataCleaning.Rmd
Fixed analysis.

#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
#load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")

load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")

@@

Everything written after this point was for the ebsco full data file (psycinof, swa, ssa).  The R objects have been all re-written and renamed.  The first thing to do is to append the ebscoFULL and proQuest objects.  Here is my recommended steps:

1.  Create a variable that takes the maximum values of the articleID from ebscoFULL
2.  Add the max value to the article ID of proQuest
3.  Write a function that matches the titles of ebscoFull with proQuest, grabs the ID, and then, eliminates the duplicates.  We have all the matching code in the original functions that you can grab.  
4.  Consider drawing on the pmatch.R function in the BWR folder.  This function forces all to lower, strips all the white space, and takes a subset of the characters (e.g., ~25 I think).  The advantage of this is to avoid the incorrect matching when colons are used.  Same title, but you get the idea of where things can go awry with title matching.  Test it extensively -- e.g., alphebatizing is also helpful.

Social work research can be really:  Bad
Social work research can be really: Bad
Social Work research can be really: bad
Social work research can be really: Bad
Social work research can be really: bad
Social Work research can be really:  bad

5.  Do necessary search and replace of subsequent code to get it working with the fully appended data file.

#Combines EbscoHost and ProQUest wrangles and eliminates duplicate article titles

```{r}

library(dplyr)

@@

# Set the working directory
#setwd("/Users/beperron/Git/SocialWorkResearch/Data")
#setwd("/Users/SSW/Documents/GitHub/SocialWork100Years/Data")
```

# Pre-processing summary
```{r echo=FALSE}
full.df$record <- ifelse(full.df$record == 
        "Social Work & Social Sciences Review",     # Spelling difference
        "Social Work and Social Sciences Review", 
                        full.df$record)

@@

full.df$record <- ifelse(full.df$record ==
    "Aretê",                                   #Spelling difference
      "Arete",
              full.df$record)

full.df$record <- ifelse(full.df$record ==
    "Journal of Gay and Lesbian Social Services",     #Spelling difference
        "Journal of Gay & Lesbian Social Services",
                        full.df$record)

full.df$record <- ifelse(full.df$record ==
    "Canadian Social Work Review/Revue canadienne de service social",
        "Canadian Social Work Review",
                        full.df$record)
```

Provided below is a summary of the datafile processed by `ebscoBWR` function before any cleaning procedures specifically for this project were employed, with the exception of resolving spelling errors or differences.  For example, _Social Work With Groups_ was exported as a separate journal than _Social Work with Groups_ (note the capitalization difference in the word _with_.)

@@

# Data cleaning

## Year specification

```{r}

year.25 <- as.character(c(1900:1987, 2014, 2015))
years <- c("2014", "2015")
#ebsco.remove <- full.df[full.df$record %in% years, ]
ebsco.remove <- full.df[full.df$record %in% year.25, ]
ebsco.remove <- ebsco.remove[, "articleID"]
full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
```

```{r exclusion1, eval=TRUE}
exclusions.1 <- c(
    "American Journal of Preventive Medicine", 
    "Behavior Modification", 
    "Brain and Cognition",
    "Canadian Journal of Community Mental Health",
    "Canadian Journal on Aging",
    "Early Child Development and Care",
    "Early Education and Development",
    "Employee Assistance Quarterly",
    "Evaluation and Program Planning",
    "General Hospital Psychiatry",
    "International Review of Social Research",
    "Journal of Applied Behavioral Science",
    "Journal of Applied Rehabilitation Counseling",
    "Journal of Community & Applied Social Psychology",
    "Journal of Health & Human Services Administration",
    "Journal of Nonverbal Behavior",
    "Journal of Psychosomatic Research",
    "Learning Disabilities Research & Practice",
    "PROFILE Issues in Teachers' Professional Development",
    "Psychotherapy",
    "Systems Research and Behavioral Science",
    "Teaching and Teacher Education",
    "The Scientific Review of Mental Health Practice",
    "The Clinical Supervisor",
    "Arete: Revista de Filosofia")

Exclusions were then made any of the three criteria

+ Journals that did not have clear evidence of a peer review process.  This was based on a review of the journals mission, scope, and whether an editorial board or group could be identified.

+ Journal titles that did not have any clear publication history based on a broad-based Internet search and other databases (e.g., ProQuest).  These exclusions are assumed to be data entry problems at time of indexing.

```{r exclusion2, eval=TRUE}
exclusions.2 <- c(
    "Eugenics and Social Welfare Bulletin",
    "Eugenics & Social Welfare Bull.",
    "Issues in Social Work Education", 
    "Hospital Social Service",  #Confirmed nursing journal
    "International Conference of Social Work",
    "Journal of Social Work Process",
    "Maatskaplike Werk/Social Work",
    "Medical Social Work",
    "New York State Department of Social Welfare, Division Publication",
    "Pediatric Social Work", 
    "Pennsylvania Social Work",
    "Proceedings of the National Conference of Social Work","Social Service",    
    "Social Service Department, Presbyterian Hospital, New York",
    "Social Service Monographs",
    "School Social Work Quarterly", 
    "Social Work Today",
    "Social Work Technique",
    "Social Work Today", 
    "Social Work Yearbook",
    "Pennsylvania Social Work",
    "University of Chicago Social Service Monograph" 
    )

>>>>

load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")

#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")

@@

# Combines EbscoHost and ProQUest

This section ... wrangles and eliminates duplicate article titles

```{r appendData, comment=NA}

@@

# Data cleaning and pre-processing

## Narrow results to past 25 years

```{r}
full.df <- ebscoBWR.df
year.25 <- as.character(c(1900:1987, 2014, 2015))
years <- c("2014", "2015")
#ebsco.remove <- full.df[full.df$record %in% years, ]
ebsco.remove <- full.df[full.df$record %in% year.25, ]
ebsco.remove <- ebsco.remove[, "articleID"]
full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
```

## Initial descriptive summary

```{r exclusion1, eval=TRUE}
exclusions.1 <- c(
    "American Journal of Preventive Medicine", 
    "Behavior Modification", 
    "Brain and Cognition",
    "Canadian Journal of Community Mental Health",
    "Canadian Journal on Aging",
    "Early Child Development and Care",
    "Early Education and Development",
    "Employee Assistance Quarterly",
    "Evaluation and Program Planning",
    "General Hospital Psychiatry",
    "International Review of Social Research",
    "Journal of Applied Behavioral Science",
    "Journal of Applied Rehabilitation Counseling",
    "Journal of Community & Applied Social Psychology",
    "Journal of Health & Human Services Administration",
    "Journal of Nonverbal Behavior",
    "Journal of Psychosomatic Research",
    "Learning Disabilities Research & Practice",
    "Professional Development in Education",
    "PROFILE Issues in Teachers' Professional Development",
    "Psychotherapy",
    "Systems Research and Behavioral Science",
    "Teaching and Teacher Education",
    "The Scientific Review of Mental Health Practice",
    "The Clinical Supervisor")

```{r exclusion2, eval=TRUE}
exclusions.2 <- c(
    "Issues in Social Work Education", 
    "Maatskaplike Werk/Social Work",
    "Pediatric Social Work", 
    "Critical Social Work"
    )

## Fix journal titles

Additional pre-processing was conducted on journal titles to resolve spelling errors or other minor title differences in the database. For example, _Social Work With Groups_ was exported as a separate journal than _Social Work with Groups_ (note the capitalization difference in the word _with_.)  We also applied a global substitution of _and_ with _&_, as this was a common source for differences.

```{r echo=FALSE}
full.df$record <- ifelse(full.df$record == 
        "Social Work & Social Sciences Review",     # Spelling difference
        "Social Work and Social Sciences Review", 
                        full.df$record)

@@

#shortens Professional Development
full.df$record <- ifelse(full.df$attributes == "journal",
        gsub(":.+", "", full.df$record), 
        full.df$record)

#shortens Canadian Social Work review by eliminating foreign title and is
#automatically combined with other short spelling
full.df$record <- ifelse(full.df$attributes == "journal",
        gsub("(/R){1}.+", "", full.df$record), 
        full.df$record)

# shortens Contemporary Rural Social Work
full.df$record <- ifelse(full.df$attributes == "journal",
        gsub("\\s\\(.+", "", full.df$record), 
        full.df$record)

full.df$record <- ifelse(full.df$attributes == "journal", 
      gsub("and", "&", full.df$record), full.df$record)

@@
